Reading main files and preparing data sets

### 2025-05-15 data-raw/03-preprocessing-main-files.Rmd
Updating data set variables to fix some columns that were wrongly classified as ordered

gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female",
                     SEX == 96 ~ "Valid skip",
                     SEX == 97 ~ "Don't know",
                     SEX == 98 ~ "Refusal",
                     SEX == 99 ~ "Not stated"), 
    SEX = factor(SEX, levels = values_ordered, ordered = TRUE))

@@

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = TRUE))

@@

gss_main_2005 <- gss_main_2005 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = TRUE))

@@

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = TRUE))

@@

gss_main_1992 <- gss_main_1992 %>% 
  mutate( # DVSEX: DVSEX of respondent
    DVSEX = 
           case_when(DVSEX == 1 ~ "Male", 
                     DVSEX == 2 ~ "Female"), 
    DVSEX = factor(DVSEX, levels = values_ordered, ordered = TRUE))

@@

gss_main_1986 <- gss_main_1986 %>% 
  mutate( # DVSEX: DVSEX of respondent
    DVSEX = 
           case_when(DVSEX == 1 ~ "Male", 
                     DVSEX == 2 ~ "Female"), 
    DVSEX = factor(DVSEX, levels = values_ordered, ordered = TRUE))

>>>>

gss_main_2015 <- gss_main_2015 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female",
                     SEX == 96 ~ "Valid skip",
                     SEX == 97 ~ "Don't know",
                     SEX == 98 ~ "Refusal",
                     SEX == 99 ~ "Not stated"), 
    SEX = factor(SEX, levels = values_ordered, ordered = FALSE))

@@

gss_main_2010 <- gss_main_2010 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = FALSE))

@@

gss_main_2005 <- gss_main_2005 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = FALSE))

@@

gss_main_1998 <- gss_main_1998 %>% 
  mutate( # SEX: Sex of respondent
    SEX = 
           case_when(SEX == 1 ~ "Male", 
                     SEX == 2 ~ "Female"), 
    SEX = factor(SEX, levels = values_ordered, ordered = FALSE))

@@

gss_main_1992 <- gss_main_1992 %>% 
  mutate( # DVSEX: DVSEX of respondent
    DVSEX = 
           case_when(DVSEX == 1 ~ "Male", 
                     DVSEX == 2 ~ "Female"), 
    DVSEX = factor(DVSEX, levels = values_ordered, ordered = FALSE))

@@

gss_main_1986 <- gss_main_1986 %>% 
  mutate( # DVSEX: DVSEX of respondent
    DVSEX = 
           case_when(DVSEX == 1 ~ "Male", 
                     DVSEX == 2 ~ "Female"), 
    DVSEX = factor(DVSEX, levels = values_ordered, ordered = FALSE))
